Improvement of Thermostated Molecular Dynamics via Backward Error Analysis

### 2018-06-07 rigid_bodies.tex
Further revision of the introduction

It seems then reasonable to argue that a NHC thermostat should regulate the shadow kinetic energy instead of the specified, ``physical'' one.
However, the theory underlying the concept of shadow Hamiltonian is only applicable to symplectic integrators, whereas NHC thermostats introduce non-Hamiltonian components to the equations of motion.
In this paper, we devise a new procedure that partially overcomes this limitation.
It consists in using a splitting-based numerical integrator that entails a Hamiltonian component, and then carrying out backward error analysis on this NVE part only.
This allows us to evaluate, with minimal computational overhead, a \textit{refined} kinetic energy for the due replacement in the thermostat equations.
It is worth mentioning that all steps of this procedure are theoretically justified.

>>>>

It seems then reasonable to argue that a NHC thermostat should regulate the shadow kinetic energy instead of the specified, ``physical'' one.
However, the theory underlying the concept of shadow Hamiltonian is only applicable to symplectic integrators, whereas NHC thermostats introduce non-Hamiltonian components to the equations of motion.
In this paper, we devise a novel procedure that partially overcomes this limitation.
It consists in using a splitting-based numerical integrator that entails a Hamiltonian component and carrying out backward error analysis on this NVE part only.
This allows us to evaluate, with minimal computational overhead, a \textit{refined kinetic energy} for replacement in the thermostat equations.
As we will demonstrate, this procedure succeeds in both predicting equipartition and reproducing a canonical ensemble consistent with the \textit{refined Hamiltonian}.
Finally, reweighting is done so that ensemble averages are consistent with the specified one.
